---
title: "Türkiye Maps"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
  output_dir: docs
baseurl: "/wb-climate-pilots-turkiye"
---

```{r setup, include=FALSE}
library(flexdashboard)
library(dplyr)
library(sf)
library(leaflet)
library(ggplot2)
```


```{r}
# Run scripts which cleans data and creates plotting functions
setwd("C:/Users/young/OneDrive/Escritorio/wb-climate-pilots-turkiye/scripts")
source("firm_data_clean.R")

setwd("C:/Users/young/OneDrive/Escritorio/wb-climate-pilots-turkiye/scripts")
source("climate_data_clean.R")
```


Location
=======================================================================

Column {.tabset .tabset-fade data-width=500}
-----------------------------------------------------------------------

### Firm location

```{r}
leaflet(firms) %>%
  
  addTiles() %>% 
  
  # Change map tiles so that locations shown in English
  addProviderTiles(providers$OpenStreetMap.DE) %>% 
  
  addAwesomeMarkers(lng = ~lon_mask, lat = ~lat_mask,
                    popup = ~paste("Region: ", a2x, "<br>",
                                   "Sector: ", stra_sector, "<br>",
                                   "Size: ", size
                    ))
```

### Number of firms in each grid

```{r}
heatplot(sf_firm_count, NULL, NULL)
```

Column {.tabset .tabset-fade data-width=500}
-----------------------------------------------------------------------

### Hot Days

```{r}
heatplot_climate(sf_hotdays, "% Change in Average Yearly Number of Hot Days\nPre (1981-2019) to Current (2020-22) Period", NULL)
```

### SPEI

```{r}
heatplot_climate(sf_spei, "% Change in Average Yearly SPEI\nPre (1981-2019) to Current (2020-22) Period", NULL)
```

### Consecutive Wet Days (5mm)

```{r}
heatplot_climate(sf_cwd, "% Change in Average Yearly Number of Consecutive Wet Days\nPre (1981-2019) to Current (2020-22) Period", NULL)
```

### Precipitation

```{r}
heatplot_climate(sf_spei, "% Change in Average Yearly Precipitation\nPre (1981-2019) to Current (2020-22) Period", NULL)
```

### Dry Days

```{r}
heatplot_climate(sf_cwd, "% Change in Average Yearly Number of Dry Days\nPre (1981-2019) to Current (2020-22) Period", NULL)
```

### Consecutive Dry Days (1mm)

```{r}
heatplot_climate(sf_spei, "% Change in Average Yearly Number of Consecutive Dry Days\nPre (1981-2019) to Current (2020-22) Period", NULL)
```


Size
=======================================================================

Column {.tabset .tabset-fade data-width=500}
-----------------------------------------------------------------------

### Average "size" (1-3 classification)

```{r}
heatplot(sf_avgsize, NULL, NULL)
```

### Average number of employees 

```{r}
heatplot(sf_avgnumemployees, NULL, NULL)
```


Column {.tabset .tabset-fade data-width=500}
-----------------------------------------------------------------------

### Hot Days

```{r}
heatplot_climate(sf_hotdays, "% Change in Average Yearly Number of Hot Days\nPre (1981-2019) to Current (2020-22) Period", NULL)
```

### SPEI

```{r}
heatplot_climate(sf_spei, "% Change in Average Yearly SPEI\nPre (1981-2019) to Current (2020-22) Period", NULL)
```

### Consecutive Wet Days (5mm)

```{r}
heatplot_climate(sf_cwd, "% Change in Average Yearly Number of Consecutive Wet Days\nPre (1981-2019) to Current (2020-22) Period", NULL)
```

### Precipitation

```{r}
heatplot_climate(sf_spei, "% Change in Average Yearly Precipitation\nPre (1981-2019) to Current (2020-22) Period", NULL)
```

### Dry Days

```{r}
heatplot_climate(sf_cwd, "% Change in Average Yearly Number of Dry Days\nPre (1981-2019) to Current (2020-22) Period", NULL)
```

### Consecutive Dry Days (1mm)

```{r}
heatplot_climate(sf_spei, "% Change in Average Yearly Number of Consecutive Dry Days\nPre (1981-2019) to Current (2020-22) Period", NULL)
```

Sectors
=======================================================================

Column {.tabset .tabset-fade data-width=500}
-----------------------------------------------------------------------

### Garments

```{r}
legend_title <- "Firms"

heatplot(sector_count("Garments"), NULL, legend_title)
```

### Other Manufacturing

```{r}
heatplot(sector_count("Other Manufacturing"), NULL, legend_title)
```

### Other Services

```{r}
heatplot(sector_count("Other Services"), NULL, legend_title)
```

### Fabricated Metal Products

```{r}
heatplot(sector_count("Fabricated Metal Products"), NULL, legend_title)
```

### Machinery & Equipment

```{r}
heatplot(sector_count("Machinery & Equipment"), NULL, legend_title)
```

### Textiles

```{r}
heatplot(sector_count("Textiles"), NULL, legend_title)
```

### Construction

```{r}
heatplot(sector_count("Construction"), NULL, legend_title)
```

### Food

```{r}
heatplot(sector_count("Food"), NULL, legend_title)
```

### Retail

```{r}
heatplot(sector_count("Retail"), NULL, legend_title)
```


Column {.tabset .tabset-fade data-width=500}
-----------------------------------------------------------------------

### Hot Days

```{r}
heatplot_climate(sf_hotdays, "% Change in Average Yearly Number of Hot Days\nPre (1981-2019) to Current (2020-22) Period", NULL)
```

### SPEI

```{r}
heatplot_climate(sf_spei, "% Change in Average Yearly SPEI\nPre (1981-2019) to Current (2020-22) Period", NULL)
```

### Consecutive Wet Days (5mm)

```{r}
heatplot_climate(sf_cwd, "% Change in Average Yearly Number of Consecutive Wet Days\nPre (1981-2019) to Current (2020-22) Period", NULL)
```

### Precipitation

```{r}
heatplot_climate(sf_spei, "% Change in Average Yearly Precipitation\nPre (1981-2019) to Current (2020-22) Period", NULL)
```

### Dry Days

```{r}
heatplot_climate(sf_cwd, "% Change in Average Yearly Number of Dry Days\nPre (1981-2019) to Current (2020-22) Period", NULL)
```

### Consecutive Dry Days (1mm)

```{r}
heatplot_climate(sf_spei, "% Change in Average Yearly Number of Consecutive Dry Days\nPre (1981-2019) to Current (2020-22) Period", NULL)
```